\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{}{Jayanth Katuri}{ % Your name
{jayanth.katuri@research.iiit.ac.in} | +91-8985747647 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.31\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\subsection{Education} 
\textbf{International Institute Of Information Technology}\\
\textbullet{}Dual Degree in Computer Science (Expected April 2018)\\
\textbullet{}Dean's List (Monsoon - 2012) \\
\textbullet{}Merit List (Spring - 2015) \\

\sectionspace % Some whitespace after the section

\subsection{Skills}

\textbf{Programming} \\
Python \textbullet{} C \textbullet{} Cpp \textbullet{} C\# \textbullet{} JS/jQuery\\
\textbf{Tools} \\
Unity 3D \textbullet{} Redis \textbullet{} Blender\\
Docker \textbullet{} Nginx \textbullet{} Django \textbullet{} Ionic\\
Kali Linux \textbullet{} Angular JS \textbullet{} Matlab \\
\textbf{Extracurricular} \\
\textbullet{} Badminton (\textit{Best Badminton Player of The Year 2016}) \textbullet{}
Cricket \textbullet{} Volleyball\\
\textbullet{} Dance (\textit{1st in group dance category, Cult Night-IIIT 2015}) \textbullet{} Guitar\\
\sectionspace % Some whitespace after the section

\subsection{Links} 

Github:// \href{https://github.com/jayanthkaturi}{\bf jayanthkaturi} \\
\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

%------------------------------------------------
% Coursework
%------------------------------------------------

\subsection{Courses}

\textbullet{}Statistical Methods in AI \\
\textbullet{}Advanced Computer Networks \\
\textbullet{}System And Network Security \\
\textbullet{}Distributed Systems \\
\textbullet{}Compilers \\
\textbullet{}Operating Systems \\
\textbullet{}Computer Programming \\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------



\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------
\subsection{Experience}

\runsubsection{Samsung Research Institute}
\descript{| Software Research Intern}

\location{May 2017 – July 2017 | Banglore, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Built a Fuzzy System in python to automatically rate a driver based on his driving skills.
\item Developed a deterministic self-driving car in Unity 3D game engine to assist data collection in environments that are difficult in real life.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Deepfence}
\descript{| Software Developer Intern}

\location{May 2016 – July 2016 | Banglore, India}
\begin{tightitemize}
\item Responsibilites include testing and debugging of different components related to micro-service architectures, distributed systems and data analytics tools.
\item Wrote several lines of code in various programming languages based on requirements.
\item Developed a golang based tool to identify vulnerabilites in docker images.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Cracku}
\descript{| Web Developer Intern}

\location{May 2015 – July 2015 | Hyderabad, India}
\begin{tightitemize}
\item Worked with Django framework and JQuery for web backend development and Ionic framework for the android application developement.
\item Added and extended several features like user profile updates, CAT interfaces for website and app, referral systems, push notifications etc.
\end{tightitemize}

%------------------------------------------------

\runsubsection{Fantasian}
\descript{| Web Developer Intern}

\location{October 2014 – December 2014 | Hyderabad, India}
\begin{tightitemize}
\item Developed a server side nodejs application to manage a game right from the initial draws for the first round to the winner declaration in the final game.
\item Used redis for maintaining scores and player information because of it's fast storage and retrievals operations.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Research
%------------------------------------------------
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\subsection{Projects}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item \descript{Deep Reinforcement Learning Agent} A scratch implementation of the Deep-Q algorithm form the famous 'Playing Atari with Deep Reinforcement Learning' paper by DeepMind. {\footnotesize \textit{\textbf{\href{https://github.com/jayanthkaturi/deepRL_agent}{Github Link} }}}
\item \descript{Emotion Detection From Facial Expressions} A keras implementation of a kaggle challenge to detect emotions on a given human face. The accuracy obtained was 52.84\% which is under top 15 of the public leaderboard when the competiton was held.{\footnotesize \textit{\textbf{\href{https://github.com/jayanthkaturi/emotion_detection}{Github Link} }}}
\item \descript{NGINX auth proxy} A fask based application for authentication of all services using nginx server. {\footnotesize \textit{\textbf{\href{https://github.com/jayanthkaturi/nginx-auth-proxy}{Github Link}}}}
\item \descript{Detection of Buffer Overflows in binary executable (IA-32 and x86-64)} Used Pin Dynamic Instrumentation tool to detect overflows, not only on return addresses, but also on the variables present on the stack and heap.
\item \descript{Compiler for Decaf Programming Language} Used flex and bison libraries to
convert a decaf program into IR (Intermediate Representation).
\item \descript{Proxy server} Socket programming project to design a proxy server.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}